\textsf{Are frontier models superhuman chemists?}

### 2024-03-11 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\subparagraph{Analytical chemistry}
The questions are sourced from the master student examination paper at the University of Jena, Germany. These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
These questions are derived from the master student examination paper at the University of Magdeburg, Germany. They explore topics related to combustion processes and engineering principles.

>>>>

\subparagraph{Analytical chemistry}
The questions are sourced from master student examination papers at the University of Jena, Germany. These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
These questions are derived from master student examination papers at the University of Magdeburg, Germany. They explore topics related to combustion processes and engineering principles.
